lifespan_eda

### 2024-03-18 eda/lifespan_eda.Rmd
fix listwise deletion

```{r}
#clean up site NAs
cn.df.imp <- cn.df.eulerfilt2 %>%
  mutate(site = trimws(as.character(site)),
         study = trimws(study)) %>%
  mutate(site = gsub(" ", "_", ifelse(is.na(site), study, paste(study, site, sep="_")))) %>%
  na.omit()

# unique(cn.df.imp$site)
# table(cn.df.imp$site, cn.df.imp$study)
# sum(is.na(cn.df.imp$site))
```

>>>>

```{r}
#clean up site NAs
cn.df.imp1 <- cn.df.eulerfilt2 %>%
  mutate(site = trimws(as.character(site)),
         study = trimws(study)) %>%
  mutate(site = gsub(" ", "_", ifelse(is.na(site), study, paste(study, site, sep="_"))))

#drop NAs listwise
cn.df.imp <- cn.df.imp1%>%
  dplyr::select(!c(INDEX.ID, country)) %>%#drop index ID for filtering
  na.omit()

skim(cn.df.imp)

nrow(cn.df.imp1) - nrow(cn.df.imp)
# unique(cn.df.imp$site)
# table(cn.df.imp$site, cn.df.imp$study)
# sum(is.na(cn.df.imp$site))
```
